Setting up Data

### 2019-11-11 src/SetupData.Rmd
re-ran set up data with updataed full MLH1 sheet

```{r mouse.table, echo=FALSE}
source("~./MLH1repo/src/CommonFunc_MLH1repo.R")

#Make a mouse level table
AP_mouse_table <- ddply(MLH1_data, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(adj_nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(adj_nMLH1.foci), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci),
                        var = format(round(   var(adj_nMLH1.foci),3), nsmall=3),
                        sd   = round(sd(adj_nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3)
                        #quality?
)

AP_mouse_table <- add_strain(AP_mouse_table)
AP_mouse_table <- add_subsp(AP_mouse_table)
AP_mouse_table <- add_sex(AP_mouse_table)
AP_mouse_table <- add_category(AP_mouse_table)

#make sure they are all factors
AP_mouse_table$mouse <- as.factor(AP_mouse_table$mouse)
AP_mouse_table$sex <- as.factor(AP_mouse_table$sex)
AP_mouse_table$strain <- as.factor(AP_mouse_table$strain)
AP_mouse_table$subsp <-  as.factor(AP_mouse_table$subsp)

#add DOB to this table?
mice.frm.meta <- AP_mouse_table[(AP_mouse_table$mouse %in% meta.data$mouse),]

#oo isn't including MLH1 means

@@

#merge with DOB
mouse.table_w.Ages <- merge(batch.mouse.count.DF, meta.data, by.y = "mouse", by.x = "Var1", all = TRUE)
AP_mouse_table_w.Ages <- merge(AP_mouse_table, meta.data, by.y = "mouse", by.x = "mouse", all = TRUE)

@@

male_mouse_table_w.Ages <- mouse.table_w.Ages[(mouse.table_w.Ages$sex == "male") &(mouse.table_w.Ages$category != "other"),]

all.ages_plot <- ggplot(male_mouse_table_w.Ages, aes(age.weeks))+geom_histogram(binwidth = 3)+facet_wrap(~category)+ggtitle("Male Age Distributions")
all.ages_plot

@@

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_9.26.19.RData")

>>>>

```{r mouse.table, echo=FALSE}
#source("~./MLH1repo/src/CommonFunc_MLH1repo.R")

#Make a mouse level table
AP_mouse_table.HQ <- ddply(MLH1_data[MLH1_data$quality < 5,], c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(adj_nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(adj_nMLH1.foci), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci),
                        var = format(round(   var(adj_nMLH1.foci),3), nsmall=3),
                        sd   = round(sd(adj_nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3)
                        #quality?
)

AP_mouse_table <- add_strain(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_subsp(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_sex(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_category(AP_mouse_table.HQ)

#make sure they are all factors
AP_mouse_table.HQ$mouse <- as.factor(AP_mouse_table.HQ$mouse)
AP_mouse_table.HQ$sex <- as.factor(AP_mouse_table.HQ$sex)
AP_mouse_table.HQ$strain <- as.factor(AP_mouse_table.HQ$strain)
AP_mouse_table.HQ$subsp <-  as.factor(AP_mouse_table.HQ$subsp)

#add DOB to this table?
mice.frm.meta <- AP_mouse_table.HQ[(AP_mouse_table.HQ$mouse %in% meta.data$mouse),]

@@

#subsp in metadata not fully correct
meta.data <- add_strain(meta.data)
meta.data <- add_subsp(meta.data)
meta.data <- add_sex(meta.data)
meta.data <- add_category(meta.data)

#merge with DOB
mouse.table_w.Ages <- merge(batch.mouse.count.DF, meta.data, by.y = "mouse", by.x = "Var1", all = TRUE)
AP_mouse_table_w.Ages <- merge(AP_mouse_table.HQ, meta.data, by.y = "mouse", by.x = "mouse", all = TRUE)
#what are the differences between these two

@@

male_mouse_table_w.Ages <- AP_mouse_table.HQ[(AP_mouse_table.HQ$sex == "male") &(mouse.table_w.Ages$category != "other"),]

all.ages_plot <- ggplot(AP_mouse_table.HQ, aes(age.weeks))+geom_histogram(binwidth = 3)+facet_wrap(~category)+ggtitle("Male Age Distributions")
all.ages_plot

@@

```{r color.scheme}
#color scheme, #mouse colors
#site for colors, #http://sape.inf.usi.ch/quick-reference/ggplot2/colour
colors_of_strains <- c('WSB'= "#56B4E9",'G' ='cadetblue','LEW'= 'lightblue','PERC'= 'blue',
                       #blues

                       'PWD'= 'red2',
                       'SKIVE'= 'coral1','KAZ'= 'coral4', 'TOM'= 'indianred1','AST' = 'red4',
                       'CZECH'= 'indianred4',

                       'MSM'= 'deeppink', 'MOLF'= 'hotpink', #mol are pinks, bc they are fancy mice

                    'CAST'='green','HMI'= 'forestgreen', #greens

                    'SPRET'='gold','SPIC'= 'goldenrod1', #browns? color of mounds?
                    'CAROLI'='gold3',

                    "F1"='grey', "other" = 'grey'
                    )

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_11.11.19.RData")
